Brownian Dynein Model

### 2015-11-03 latex/derivation.tex
Add Xnm derivative, todo: Ynm, Xfm, Yfm

\begin{align}
  X_{nm} &= L_{s}\Bigg( \Big(\frac{L^2+L_{n}^2-L_{f}^2}{2LL_{n}}\Big)\Big(\frac{L_{s}^2+L_{n}^2-L_{t}^2}{2L_{s}L_{n}}\Big) \mp \sqrt{1-\bigg(\frac{L^2+L_{n}^2-L_{f}^2}{2LL_{n}}\bigg)^2}\sqrt{1-\bigg(\frac{L_{s}^2+L_{n}^2-L_{t}^2}{2L_{s}L_{n}}\bigg)^2} \Bigg) \\
  Y_{nm} &= L_{s}\Bigg(\frac{L_{s}^2+L_{n}^2-L_{t}^2}{2L_{s}L_{n}}\sqrt{1-\bigg(\frac{L^2+L_{n}^2-L_{f}^2}{2LL_{n}}\bigg)^2} \pm \frac{L^2+L_{n}^2-L_{f}^2}{2LL_{n}}\sqrt{1-\bigg(\frac{L_{s}^2+L_{n}^2-L_{t}^2}{2L_{s}L_{n}}\bigg)^2} \Bigg) \\
\end{align}

@@

@@

\subsection{$X_t$ and $Y_t$}

\begin{align}
  X_{t} &= L_n\cos(\Theta_{1}) \\
       &= \frac{L^2+L_n^2-L_f^2}{2L} \\
\end{align}

\begin{align}
  Y_{t} &= L_n\sin(\Theta_{1}) \\
  &= L_n\sin(\cos^{-1}(\frac{L^2+L_n^2-L_f^2}{2LL_n})) \\
  &= L_n\sqrt{1 - \big(\frac{(L^2+L_n^2-L_f^2}{2LL_n}\big)^2} \\
\end{align}

@@

\begin{align}
  Y_{nb} &= 0 \\
  Y_{nm} &=  \\
  Y_{t}  &= L_n\sqrt{1 - \big(\frac{(L^2+L_n^2-L_f^2}{2LL_n}\big)^2} \\
  Y_{fm} &=  \\
  Y_{fb} &= 0
\end{align}

\section{Cartesian Velocities}
This section shows the velocity definitions. \\
\begin{align}
  \dot{X}_{nb} &= 0 \\
  \dot{X}_{nm} &= \\
  \dot{X}_{t } &= \frac{L^2+2L_n\dot{L}_n-2L_f\dot{L}_f}{2L} \\
  \dot{X}_{fm} &= \\
  \dot{X}_{fb} &= 0
\end{align}

\begin{align}                                                                          
  \dot{Y}_{nb} &= 0 \\                                         
  \dot{Y}_{nm} &= \\
  \dot{Y}_{t}  &= \frac{L_n}{2\sqrt{1 - \big(\frac{(L^2+L_n^2-L_f^2}{2LL_n}\big)^2}} * \big(\frac{(-L^2L_n^{-2}+\dot{L}_n - 2L_f\dot{L}_nL_n^{-1} + L_f^2L_n^{-2}}{2L}\big) - think this is rite?\\
  \dot{Y}_{fm} &= \\
  \dot{Y}_{fb} &= 0 \\
\end{align}

>>>>

\begin{align}
  X_{nm} &= L_{s}\Bigg( \Big(\frac{L^2+L_{n}^2-L_{f}^2}{2LL_{n}}\Big)\Big(\frac{L_{s}^2+L_{n}^2-L_{t}^2}{2L_{s}L_{n}}\Big) \mp \sqrt{1-\bigg(\frac{L^2+L_{n}^2-L_{f}^2}{2LL_{n}}\bigg)^2}\sqrt{1-\bigg(\frac{L_{s}^2+L_{n}^2-L_{t}^2}{2L_{s}L_{n}}\bigg)^2} \Bigg)\\
  Y_{nm} &= L_{s}\Bigg(\frac{L_{s}^2+L_{n}^2-L_{t}^2}{2L_{s}L_{n}}\sqrt{1-\bigg(\frac{L^2+L_{n}^2-L_{f}^2}{2LL_{n}}\bigg)^2} \pm \frac{L^2+L_{n}^2-L_{f}^2}{2LL_{n}}\sqrt{1-\bigg(\frac{L_{s}^2+L_{n}^2-L_{t}^2}{2L_{s}L_{n}}\bigg)^2} \Bigg)\\
\end{align}

@@

\begin{align}
  \dot{X}_{nm} &= \frac{-L_s^2L^2 - L_n^2L^2 + L_t^2L^2 - L_s^2L_{n}^2 - L_n^2L_{n}^2 + L_t^2L_{n}^2 + L_s^2L_{f}^2 + L_n^2L_{f}^2 - L_t^2L_{f}^2}{{2L_n^{3}LL_s}}\dot{L}_n\\ &+ \frac{2L_nL^2\dot{L}_n + 2L_s^2L_{n}\dot{L}_n + 4L_n^3\dot{L}_n - 2L_t^2L_{n}\dot{L}_n - 2L_s^2L_{f}\dot{L}_f - 2L_nL_{f}^2\dot{L}_n - 2L_n^2L_{f}\dot{L}_f + 2L_t^2L_{f}\dot{L}_f}{4L_n^2LL_s}\\
  &\mp L_s\frac{\left(\frac{L^4 + L_n^2L^2 - L_f^2L^2 + L^2L_{n}^2 + L_{n}^4 - L_f^2L_{n}^2 - L^2L_{f}^2 + L_n^2L_{f}^2 + L_{f}^4}{2LL^2_{n}} - \frac{2L_nL^2\dot{L}_n - 2L_fL^2\dot{L}_f + 2L^2L_{n}\dot{L}_n + 4L_{n}^3\dot{L}_n - 2L^2L_{f}\dot{L}_f  + 4L_{f}^3\dot{L}_f}{2LL_{n}}\right)}{2\sqrt{1-\frac{L^4 + L_n^2L^2 - L_f^2L^2 + L^2L_{n}^2 + L_{n}^4 - L_f^2L_{n}^2 - L^2L_{f}^2 + L_n^2L_{f}^2 + L_{f}^4}{2LL_{n}}}}*\\
  &\sqrt{1-\frac{L_{s}^4 + L_n^2L_{s}^2 - L_t^2L_{s}^2 + L_s^2L_{n}^2 + L_{n}^4 - L_t^2L_{n}^2 - L_s^2L_{t}^2 - L_n^2L_{t}^2 + L_{t}^4}{2L_{s}L_{n}}}\\
  &\mp L_s\sqrt{1-\frac{L^4 + L_n^2L^2 - L_f^2L^2 + L^2L_{n}^2 + L_{n}^4 - L_f^2L_{n}^2 - L^2L_{f}^2 + L_n^2L_{f}^2 + L_{f}^4}{2LL_{n}}}*\\
  &\frac{\left(\frac{L_{s}^4 + L_n^2L_{s}^2 - L_t^2L_{s}^2 + L_s^2L_{n}^2 + L_{n}^4 - L_t^2L_{n}^2 - L_s^2L_{t}^2 - L_n^2L_{t}^2 + L_{t}^4}{2L_{s}L^2_{n}}\dot{L}_n
    - \frac{2L_nL_{s}^2\dot{L}_n + 2L_s^2L_{n}\dot{L}_n + 4L_{n}^3\dot{L}_n - 2L_t^2L_{n}\dot{L}_n - 2L_nL_{t}^2\dot{L}_n}{2L_{s}L_{n}}\right)}{2\sqrt{1-\frac{L_{s}^4 + L_n^2L_{s}^2 - L_t^2L_{s}^2 + L_s^2L_{n}^2 + L_{n}^4 - L_t^2L_{n}^2 - L_s^2L_{t}^2 - L_n^2L_{t}^2 + L_{t}^4}{2L_{s}L_{n}}}}\\
\end{align}

\begin{align}
  \dot{X}_{nm} &= \frac{-L_s^2L^2 - L_n^2L^2 + L_t^2L^2 - L_s^2L_{n}^2 - L_n^2L_{n}^2 + L_t^2L_{n}^2 + L_s^2L_{f}^2 + L_n^2L_{f}^2 - L_t^2L_{f}^2}{{2L_n^{3}LL_s}}\dot{L}_n\\
  &+ \frac{2L_nL^2 + 2L_s^2L_{n} + 4L_n^3 - 2L_t^2L_{n} - 2L_nL_{f}^2\dot{L}_n}{4L_n^2LL_s}\dot{L}_n + \frac{-2L_s^2L_{f} - 2L_n^2L_{f} + 2L_t^2L_{f}}{4L_n^2LL_s}\dot{L}_f\\
  &\mp L_s\frac{\left(\frac{L^4 + L_n^2L^2 - L_f^2L^2 + L^2L_{n}^2 + L_{n}^4 - L_f^2L_{n}^2 - L^2L_{f}^2 + L_n^2L_{f}^2 + L_{f}^4}{2LL^2_{n}} - \frac{2L_nL^2 + 2L^2L_{n} + 4L_{n}^3}{2LL_{n}}\right)}{2\sqrt{1-\frac{L^4 + L_n^2L^2 - L_f^2L^2 + L^2L_{n}^2 + L_{n}^4 - L_f^2L_{n}^2 - L^2L_{f}^2 + L_n^2L_{f}^2 + L_{f}^4}{2LL_{n}}}}*\\
  &\sqrt{1-\frac{L_{s}^4 + L_n^2L_{s}^2 - L_t^2L_{s}^2 + L_s^2L_{n}^2 + L_{n}^4 - L_t^2L_{n}^2 - L_s^2L_{t}^2 - L_n^2L_{t}^2 + L_{t}^4}{2L_{s}L_{n}}}\dot{L}_n\\
  &\mp L_s\frac{\left(-\frac{-2L_fL^2 - 2L^2L_{f} + 4L_{f}^3}{2LL_{n}}\right)}{2\sqrt{1-\frac{L^4 + L_n^2L^2 - L_f^2L^2 + L^2L_{n}^2 + L_{n}^4 - L_f^2L_{n}^2 - L^2L_{f}^2 + L_n^2L_{f}^2 + L_{f}^4}{2LL_{n}}}}*\\
  &\sqrt{1-\frac{L_{s}^4 + L_n^2L_{s}^2 - L_t^2L_{s}^2 + L_s^2L_{n}^2 + L_{n}^4 - L_t^2L_{n}^2 - L_s^2L_{t}^2 - L_n^2L_{t}^2 + L_{t}^4}{2L_{s}L_{n}}}\dot{L}_f\\
  &\mp L_s\sqrt{1-\frac{L^4 + L_n^2L^2 - L_f^2L^2 + L^2L_{n}^2 + L_{n}^4 - L_f^2L_{n}^2 - L^2L_{f}^2 + L_n^2L_{f}^2 + L_{f}^4}{2LL_{n}}}*\\
  &\frac{\left(\frac{L_{s}^4 + L_n^2L_{s}^2 - L_t^2L_{s}^2 + L_s^2L_{n}^2 + L_{n}^4 - L_t^2L_{n}^2 - L_s^2L_{t}^2 - L_n^2L_{t}^2 + L_{t}^4}{2L_{s}L^2_{n}}
    - \frac{2L_nL_{s}^2 + 2L_s^2L_{n} + 4L_{n}^3 - 2L_t^2L_{n} - 2L_nL_{t}^2}{2L_{s}L_{n}}\right)}{2\sqrt{1-\frac{L_{s}^4 + L_n^2L_{s}^2 - L_t^2L_{s}^2 + L_s^2L_{n}^2 + L_{n}^4 - L_t^2L_{n}^2 - L_s^2L_{t}^2 - L_n^2L_{t}^2 + L_{t}^4}{2L_{s}L_{n}}}}\dot{L}_n\\
\end{align}

\begin{align}
  \dot{X}_{nm} &= \Bigg(\frac{-L_s^2L^2 - L_n^2L^2 + L_t^2L^2 - L_s^2L_{n}^2 - L_n^2L_{n}^2 + L_t^2L_{n}^2 + L_s^2L_{f}^2 + L_n^2L_{f}^2 - L_t^2L_{f}^2}{{2L_n^{3}LL_s}}\\
  &+ \frac{2L_nL^2 + 2L_s^2L_{n} + 4L_n^3 - 2L_t^2L_{n} - 2L_nL_{f}^2\dot{L}_n}{4L_n^2LL_s}\dot{L}_n\\
  &\mp L_s\frac{\left(\frac{L^4 + L_n^2L^2 - L_f^2L^2 + L^2L_{n}^2 + L_{n}^4 - L_f^2L_{n}^2 - L^2L_{f}^2 + L_n^2L_{f}^2 + L_{f}^4}{2LL^2_{n}} - \frac{2L_nL^2 + 2L^2L_{n} + 4L_{n}^3}{2LL_{n}}\right)}{2\sqrt{1-\frac{L^4 + L_n^2L^2 - L_f^2L^2 + L^2L_{n}^2 + L_{n}^4 - L_f^2L_{n}^2 - L^2L_{f}^2 + L_n^2L_{f}^2 + L_{f}^4}{2LL_{n}}}}*\\
  &\sqrt{1-\frac{L_{s}^4 + L_n^2L_{s}^2 - L_t^2L_{s}^2 + L_s^2L_{n}^2 + L_{n}^4 - L_t^2L_{n}^2 - L_s^2L_{t}^2 - L_n^2L_{t}^2 + L_{t}^4}{2L_{s}L_{n}}}\\
  &\mp L_s\sqrt{1-\frac{L^4 + L_n^2L^2 - L_f^2L^2 + L^2L_{n}^2 + L_{n}^4 - L_f^2L_{n}^2 - L^2L_{f}^2 + L_n^2L_{f}^2 + L_{f}^4}{2LL_{n}}}*\\
  &\frac{\left(\frac{L_{s}^4 + L_n^2L_{s}^2 - L_t^2L_{s}^2 + L_s^2L_{n}^2 + L_{n}^4 - L_t^2L_{n}^2 - L_s^2L_{t}^2 - L_n^2L_{t}^2 + L_{t}^4}{2L_{s}L^2_{n}}
    - \frac{2L_nL_{s}^2 + 2L_s^2L_{n} + 4L_{n}^3 - 2L_t^2L_{n} - 2L_nL_{t}^2}{2L_{s}L_{n}}\right)}{2\sqrt{1-\frac{L_{s}^4 + L_n^2L_{s}^2 - L_t^2L_{s}^2 + L_s^2L_{n}^2 + L_{n}^4 - L_t^2L_{n}^2 - L_s^2L_{t}^2 - L_n^2L_{t}^2 + L_{t}^4}{2L_{s}L_{n}}}}\Bigg)\dot{L}_n\\
  &+ \Bigg(\frac{-2L_s^2L_{f} - 2L_n^2L_{f} + 2L_t^2L_{f}}{4L_n^2LL_s} \mp L_s\frac{\left(-\frac{-2L_fL^2 - 2L^2L_{f} + 4L_{f}^3}{2LL_{n}}\right)}{2\sqrt{1-\frac{L^4 + L_n^2L^2 - L_f^2L^2 + L^2L_{n}^2 + L_{n}^4 - L_f^2L_{n}^2 - L^2L_{f}^2 + L_n^2L_{f}^2 + L_{f}^4}{2LL_{n}}}}*\\
  &\sqrt{1-\frac{L_{s}^4 + L_n^2L_{s}^2 - L_t^2L_{s}^2 + L_s^2L_{n}^2 + L_{n}^4 - L_t^2L_{n}^2 - L_s^2L_{t}^2 - L_n^2L_{t}^2 + L_{t}^4}{2L_{s}L_{n}}}\Bigg)\dot{L}_f\\
\end{align}

@@

\subsection{Solving for $X_t$ and $Y_t$}

\begin{align}
  X_{t} &= L_n\cos(\Theta_{1}) \\
  &= \frac{L^2+L_n^2-L_f^2}{2L} \\
  \dot{X}_t &= \frac{L_n}{L}\dot{L}_n - \frac{L_f}{L}\dot{L}_f\\
\end{align}

\begin{align}
  Y_{t} &= L_n\sin(\Theta_{1}) \\
  &= L_n\sin\left(\cos^{-1}\left(\frac{L^2+L_n^2-L_f^2}{2LL_n}\right)\right) \\
  &= L_n\sqrt{1 - \left(\frac{L^2+L_n^2-L_f^2}{2LL_n}\right)^2} \\
  &= \sqrt{L_n^2 - \left(\frac{L^2+L_n^2-L_f^2}{2L}\right)^2} \\
  \dot{Y}_t &= \frac{2L_n\dot{L}_n - \left(\frac{L^2+L_n^2-L_f^2}{L}\right)\left(\frac{L_n\dot{L}_n - L_f\dot{L}_f}{L}\right)}{2\sqrt{L_n^2 - \left(\frac{L^2+L_n^2-L_f^2}{2L}\right)^2}}\\
  \dot{Y}_t &= \frac{2L_n - \left(\frac{L^2+L_n^2-L_f^2}{L}\right)\left(\frac{L_n}{L}\right)}{2\sqrt{L_n^2 - \left(\frac{L^2+L_n^2-L_f^2}{2L}\right)^2}}\dot{L}_n +
  \frac{\left(\frac{L^2+L_n^2-L_f^2}{L}\right)\left(\frac{L_f}{L}\right)}{2\sqrt{L_n^2 - \left(\frac{L^2+L_n^2-L_f^2}{2L}\right)^2}}\dot{L}_f\\
\end{align}

@@

\begin{align}
  Y_{nb} &= 0 \\
  Y_{nm} &=  \\
  Y_{t}  &= L_n\sqrt{1 - \left(\frac{(L^2+L_n^2-L_f^2}{2LL_n}\right)^2} \\
  Y_{fm} &=  \\
  Y_{fb} &= 0
\end{align}

\section{Cartesian Velocities}
This section shows the velocity definitions. \\

\textbf{REFORMAT!}

\begin{align}
  A_{xn} &= \Bigg(\frac{-L_s^2L^2 - L_n^2L^2 + L_t^2L^2 - L_s^2L_{n}^2 - L_n^2L_{n}^2 + L_t^2L_{n}^2 + L_s^2L_{f}^2 + L_n^2L_{f}^2 - L_t^2L_{f}^2}{{2L_n^{3}LL_s}}\\
  &+ \frac{2L_nL^2 + 2L_s^2L_{n} + 4L_n^3 - 2L_t^2L_{n} - 2L_nL_{f}^2\dot{L}_n}{4L_n^2LL_s}\dot{L}_n\\
  &\mp L_s\frac{\left(\frac{L^4 + L_n^2L^2 - L_f^2L^2 + L^2L_{n}^2 + L_{n}^4 - L_f^2L_{n}^2 - L^2L_{f}^2 + L_n^2L_{f}^2 + L_{f}^4}{2LL^2_{n}} - \frac{2L_nL^2 + 2L^2L_{n} + 4L_{n}^3}{2LL_{n}}\right)}{2\sqrt{1-\frac{L^4 + L_n^2L^2 - L_f^2L^2 + L^2L_{n}^2 + L_{n}^4 - L_f^2L_{n}^2 - L^2L_{f}^2 + L_n^2L_{f}^2 + L_{f}^4}{2LL_{n}}}}*\\
  &\sqrt{1-\frac{L_{s}^4 + L_n^2L_{s}^2 - L_t^2L_{s}^2 + L_s^2L_{n}^2 + L_{n}^4 - L_t^2L_{n}^2 - L_s^2L_{t}^2 - L_n^2L_{t}^2 + L_{t}^4}{2L_{s}L_{n}}}\\
  &\mp L_s\sqrt{1-\frac{L^4 + L_n^2L^2 - L_f^2L^2 + L^2L_{n}^2 + L_{n}^4 - L_f^2L_{n}^2 - L^2L_{f}^2 + L_n^2L_{f}^2 + L_{f}^4}{2LL_{n}}}*\\
  &\frac{\left(\frac{L_{s}^4 + L_n^2L_{s}^2 - L_t^2L_{s}^2 + L_s^2L_{n}^2 + L_{n}^4 - L_t^2L_{n}^2 - L_s^2L_{t}^2 - L_n^2L_{t}^2 + L_{t}^4}{2L_{s}L^2_{n}}
    - \frac{2L_nL_{s}^2 + 2L_s^2L_{n} + 4L_{n}^3 - 2L_t^2L_{n} - 2L_nL_{t}^2}{2L_{s}L_{n}}\right)}{2\sqrt{1-\frac{L_{s}^4 + L_n^2L_{s}^2 - L_t^2L_{s}^2 + L_s^2L_{n}^2 + L_{n}^4 - L_t^2L_{n}^2 - L_s^2L_{t}^2 - L_n^2L_{t}^2 + L_{t}^4}{2L_{s}L_{n}}}}\Bigg)\\
  A_{xf} &= \Bigg(\frac{-2L_s^2L_{f} - 2L_n^2L_{f} + 2L_t^2L_{f}}{4L_n^2LL_s} \mp L_s\frac{\left(-\frac{-2L_fL^2 - 2L^2L_{f} + 4L_{f}^3}{2LL_{n}}\right)}{2\sqrt{1-\frac{L^4 + L_n^2L^2 - L_f^2L^2 + L^2L_{n}^2 + L_{n}^4 - L_f^2L_{n}^2 - L^2L_{f}^2 + L_n^2L_{f}^2 + L_{f}^4}{2LL_{n}}}}*\\
  &\sqrt{1-\frac{L_{s}^4 + L_n^2L_{s}^2 - L_t^2L_{s}^2 + L_s^2L_{n}^2 + L_{n}^4 - L_t^2L_{n}^2 - L_s^2L_{t}^2 - L_n^2L_{t}^2 + L_{t}^4}{2L_{s}L_{n}}}\Bigg)\\
  B_{xn} &= \frac{L_n}{L}\\
  B_{xf} &= -\frac{L_f}{L}\\
  C_{xn} &= \\
  C_{xf} &= \\
  A_{yn} &= \\
  A_{yf} &= \\
  B_{yn} &= \frac{2L_n - \left(\frac{L^2+L_n^2-L_f^2}{L}\right)\left(\frac{L_n}{L}\right)}{2\sqrt{L_n^2 - \left(\frac{L^2+L_n^2-L_f^2}{2L}\right)^2}}\\
  B_{yf} &= \frac{\left(\frac{L^2+L_n^2-L_f^2}{L}\right)\left(\frac{L_f}{L}\right)}{2\sqrt{L_n^2 - \left(\frac{L^2+L_n^2-L_f^2}{2L}\right)^2}}\\
  C_{yn} &= \\
  C_{yf} &= \\
\end{align}

\begin{align}
  \dot{X}_{nb} &= 0 \\
  \dot{X}_{nm} &= A_{xn}\dot{L}_n + A_{xf}\dot{L}_f\\
  \dot{X}_{t } &= B_{xn}\dot{L}_n + B_{xf}\dot{L}_f\\
  \dot{X}_{fm} &= C_{xn}\dot{L}_n + C_{xf}\dot{L}_f\\
  \dot{X}_{fb} &= 0
\end{align}

\begin{align}                                                                          
  \dot{Y}_{nb} &= 0 \\                           
  \dot{Y}_{nm} &= A_{yn}\dot{L}_n + A_{yf}\dot{L}_f\\
  \dot{Y}_{t}  &= B_{yn}\dot{L}_n + B_{yf}\dot{L}_f\\
  \dot{Y}_{fm} &= C_{yn}\dot{L}_n + C_{yf}\dot{L}_f\\
  \dot{Y}_{fb} &= 0 \\
\end{align}
